---
title: "README"
author: "Mirza Cengic"
date: '23 mart 2018 '
output: rmarkdown::github_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "README_figures/")
```

# speciesrangeR - species range maps in R

This repository hold skeleton functions to retrieve species data from GBIF and create species ranges. Functions will eventually be migrated into a package.
This repo serves as a **proof of concept** for [GSoC 2018 proposal](https://github.com/rstats-gsoc/gsoc2018/wiki/Species-range-maps-in-R).

#### Tasks to solve:  
* Easy: write a script to download occurrence data from GBIF for a species and
display them on a map.  

* Medium: Draw a convex hull polygon around the points in the earlier test.  

* Hard: Clip the polygon you generated in medium test to world
map (Keep only part of the polygon which is on land).  

```{r script_setup, echo=TRUE}
if(!require(pacman))
{
  install.packages("pacman")
}

pacman::p_load(spocc, sf, mapview, lubridate, dplyr, raster, tictoc,
               sf, scrubr, stringr, sp, rgeos, dismo, broom, tmap)
```


## Working with speciesrangeR
We will load here speciesrangeR package. Temporarily it is a set of scripts that can be sourced, but will be replaced with package that can be installed via devtools. Use get_species_data() to query [GBIF](https://www.gbif.org/). Function is a wrapper around occ() function from [spocc](https://ropensci.github.io/spocc/) package.

```{r pressure, echo=TRUE}
source("Y:/Mirza_Cengic/Projects/Other/GSoC/R/get_species_data.R")

sal_atra_ita <- get_species_data("Salamandra atra", return_clean = TRUE, 
                                 return = "sp", country = "ITA")

# Plot maps
# mapview(sal_atra_ita)
sal_atra_map <- mapview(sal_atra_ita)
mapshot(sal_atra_map, file = "map.png")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
